---
title: "PVA Report"

author: "Report generated at https://tumor-volume.jax.org"

date: '`r format(Sys.time(), "%d %B, %Y")`'

header-includes:
    \usepackage{booktabs}
    \usepackage{colortbl}
    \usepackage{caption}
    \usepackage{float}
    \floatplacement{figure}{H}
    
geometry: "left=3cm,right=3cm,top=2cm,bottom=2cm"

output:
    html_document:
        toc: true
        toc_float:
            collapsed: false
        toc_depth: 4
        theme: cerulean
        fig_width: 9
        fig_height: 7
        fig.caption: true
        code_folding: 'hide'
        df_print: kable
    pdf_document:
        toc: true
        toc_depth: 5
        fig_width: 9
        fig_height: 7
        df_print: kable

always_allow_html: true

params:
    data_subset: NA
    tv_all_plot_type: NA
    tv_all_plot_style: NA
    tv_all_interpolate: NA
    tv_all_plotType: NA
    tv_all_scaleby: NA
    tv_all_endpoint_scale: NA
    main_avgplot_interpolate: NA
    main_avgplot.day: NA
    main_log2fold.day: NA
    main_log2_interpolate: NA
    main_TC.day: NA
    main_tc_interpolate: NA
    main_TGI.day: NA
    main_tgi_interpolate: NA
    main_orc.day: NA
    main_stackedorc_interpolate: NA
    tv_recist.day: NA
    tv_study_filtered: NA
    tv_interpolate: NA
    waterfall_metric: NA
    tv_AUC.day.waterfall: NA
    tv_waterfall_interpolate: NA
    tv_PercChange_EventSize: NA
    anova_Measure_Day: NA
    tv_tumor_filtered: NA
    main_anova_interpolate: NA
    tv_weight_plot_type: NA
    tv_weight_plot_style: NA
    tv_weight_plotType: NA
    script_location: NA
    progress: NA
---

\newpage

## Report Summary

```{r load options and functions, results='hide', echo=FALSE}
    
    knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
    
    source(params$script_location, local = knitr::knit_global())

    suppressPackageStartupMessages({
        library("shiny")
        library("plotly")
        library("dygraphs")
        library("shinyWidgets")
        library("plyr")
        library("dplyr")
        library("zoo")
        library("ggpubr")
        library("grid")
        library("gridExtra")
        library("gtable")
        library("shinydashboard")
        library("reactable")
        library("bcrypt")
        library("shinyBS")
        library("shinyjs")
        library("shinyFeedback")
        library("shinycssloaders")
        library("shinyAce")
        library("jsonlite")
        library("magrittr")
        library("knitr")
        library("DT")
        library("readxl")
        library("survival")
        library("survminer")
        library("validate")
        library("multcomp")
        library("validate")
        library("purrr")
        library("stringr")
        library("shinyalert")
        library("kableExtra")
        library(promises)
        library(future)
    })

    set.seed(42)

```

```{css, echo=FALSE}
.main-container {
  max-width: 1500px !important;
  margin: auto;
  padding: 1em;
  line-height: 20px ; 
}   
```

```{r, echo=FALSE}
# print(params)

# Stub code for adding plots / tables. from main data

# ```{r code stubs}

#     plot_data <- params$data_subset

#     # shiny::setProgress(0.3)
# ```

# Stub code for adding plots /tables from single selected studies

# ```{r }

#     df <- base::subset(
#     params$data_subset, Study %in% c(params$tv_study_filtered)
#     )
    
#     # shiny::setProgress(0.3)
# ```

```

```{r, results='asis', echo=FALSE}

cat("This report was generated with the PVA tool on: ", format(Sys.time(), "%m.%d.%Y at %Hh:%Mm"), '\n\n\n')

cat("Included in this report is data from ",
    length(unique(params$data_subset$"Contributor")),
    "contributing institution(s), ",
    length(unique(params$data_subset$"ID")),
    "individual animals, ",
    length(unique(params$data_subset$"Study")),
    "study group(s), ",
    length(unique(params$data_subset$"Tumor")),
    "tumor(s) [model(s)] from ",
    length(unique(params$data_subset$"Disease_Type")),
    "disease type(s), which were treated with ",
    length(unique(params$data_subset$"Arms")),
    "agents (control included in count).\n\n\n")


    cat("The contributing institution(s) present are: ",
        paste(shQuote(levels(as.factor(params$data_subset$"Contributor"))), collapse = ", "),
        "\n\n\n")

    cat("The study group(s) present are: ",
        paste(shQuote(levels(as.factor(params$data_subset$"Study"))), collapse = ", "),
        "\n\n\n")

    cat("The tumor(s) [model(s)] present are: ",
        paste(shQuote(levels(as.factor(params$data_subset$"Tumor"))), collapse = ", "),
        "\n\n\n")

    cat("The disease type(s) present are: ",
        paste(shQuote(levels(as.factor(params$data_subset$"Tumor"))), collapse = ", "),
        "\n\n\n")

    cat("The agents present are: ",
        paste(shQuote(levels(as.factor(params$data_subset$"Arms"))), collapse = ", "),
        "\n\n\n")

```

\newpage

## Cross Study Plots & Analysis

A Summary of cross study plots and analyses.

### Response Plot

```{r base volume plot, fig.align='center', echo=FALSE}
 
    plot_data <- params$data_subset

    if (params$tv_all_plot_type == "Treatment Plot") {
        pattern_type <- "Treatment"
    } else if (params$tv_all_plot_type == "Study Plot") {
        pattern_type <- "Study"
    }

    if (params$tv_all_plot_style == "Study Average") {
        level_type <- "Arm"
    } else if (params$tv_all_plot_style == "Individual Animal") {
        level_type <- "Animal"
    }
    # interpolate the data if asked for.
    if (params$tv_all_interpolate){
        plot_data = get_interpolated_pdx_data(data = plot_data)
        plot_data$Volume <- plot_data$Interpolated_Volume
    }

        #Adjust the data to semi-log if asked for.
    if (params$tv_all_plotType == 'Log2(Volume)'){
        plot_data$Volume <- log2(1 + plot_data$Volume)

        # Adjust the data to percent change the data if asked for
    } else if (params$tv_all_plotType == 'Percent Change') {
        plot_data <- plot_data %>%
            dplyr::arrange(Contributor, Study, Tumor, Arms, ID, Times) %>%
            dplyr::group_by(Contributor, Study, Tumor, Arms, ID) %>%
            dplyr::mutate(dVt = (((Volume - Volume[1]) / Volume[1] ) * 100))
        plot_data$Volume <- plot_data$dVt

        # Adjust to semi-log of prop change if asked for
    } else if (params$tv_all_plotType == 'Log2(Proportion Volume Change)') {
        plot_data <- plot_data %>%
            dplyr::arrange(Contributor, Study, Tumor, Arms, ID, Times) %>%
            dplyr::group_by(Contributor, Study, Tumor, Arms, ID) %>%
            dplyr::mutate(log2.dVt = log2(1 + ((Volume - Volume[1]) / Volume[1])))
        plot_data$Volume <- plot_data$log2.dVt
    }

    # Call plot
    if (params$tv_all_plotType == 'Scaled') {
        if(params$tv_all_scaleby == "Volume") {
        scale_by_volume_all <- TRUE

        tv_all_text_scaled <- renderText({
            paste0("Plots are scaled by Volume. Y-axis ranges from 100% with endpoint scaling of ",
                params$tv_all_endpoint_scale,
                "mm3 to -100% (total regression)")
        })

        } else {
        scale_by_volume_all <- FALSE

        tv_all_text_scaled <- renderText({
            paste0("Plots are scaled by Relative Growth. Y-axis ranges from 100% with endpoint scaling of ",
                params$tv_all_endpoint_scale,
                "x starting growth to -100% (total regression)")
        })
        }

        endpoint_scale_all <- params$tv_all_endpoint_scale

        get_plot_scaled(data = plot_data, position.dodge = 0.2,  title = NULL, scale.factor = endpoint_scale_all, scale.by.volume = scale_by_volume_all, level = level_type, pattern = pattern_type, tv_all_plotType = params$tv_all_plotType)

    } else {

        # Reset Info Text of the Scaled Plot
        tv_all_text_scaled <- renderText({""})

        get_tv_plot(data = plot_data, level = level_type, pattern = pattern_type, position.dodge = 0.2, tv_all_plotType = params$tv_all_plotType)
    }
    
    params$progress$inc(1 / 10)
```

```{r response plot option text, results='asis', echo=FALSE}

    cat("The response plot metric: ")
    cat(paste("**",params$tv_all_plotType,"**",sep=""))
    cat(", was faceted by: ")
    cat(paste("**",params$tv_all_plot_type,"**",sep=""))
    cat(", plots were organized by: ")
    cat(paste("**",params$tv_all_plot_style,"**. ",sep=""))

    if (params$tv_all_plotType == 'Scaled') {
        if(params$tv_all_scaleby == "Volume") {        
            cat(paste0("Plots are scaled by **Volume**. Y-axis ranges from 100% with endpoint scaling of ",
                "**",params$tv_all_endpoint_scale,"**",
                "**mm3** to -100% (total regression). "))
        } else {
            cat(paste0("Plots are scaled by **Relative Growth**. Y-axis ranges from 100% with endpoint scaling of ",
                "**",params$tv_all_endpoint_scale,"**",
                "**x** starting growth to -100% (total regression). "))
        }
    }

    if (params$tv_all_interpolate) {
        print("Data were interpolated for this plot.")
    }

```

### Average Volume Plot

```{r avg volume plot, fig.align='center', echo=FALSE}
    
    plot_data <- params$data_subset

    if (params$main_avgplot_interpolate){
        plot_data <- get_interpolated_pdx_data(data = plot_data)
        plot_data$Volume <- plot_data$Interpolated_Volume
    }

    tc_ratios <- T.C_ratio(plot_data, last.measure.day = params$main_avgplot.day)

    plotAvgGrowthBar(tc_ratios)

```

```{r average plot option text, results='asis', echo=FALSE}

    cat("The average response plot was computed on (or near) day: ")
    cat(paste("**",params$main_avgplot.day,"**.",sep=""))

    if (params$main_avgplot_interpolate) {
        print("Data were interpolated for this plot.")
    }

```

### Log2 Fold Change Plot

```{r log2_foldchange, fig.align='center', echo=FALSE}

    plot_data <- params$data_subset


    if (params$main_log2_interpolate){
        plot_data <- get_interpolated_pdx_data(data = plot_data)
        plot_data$Volume <- plot_data$Interpolated_Volume
    }

    vc_change <- IndividualMouseResponse(plot_data, last.measure.day = params$main_log2fold.day)

    log2FoldPlot(vc_change, caption_text_on = F, point_size = 1)

    params$progress$inc(1 / 10)
```

```{r log2 fold change plot option text, results='asis', echo=FALSE}

    cat("The log2 fold change plot was computed on (or near) day: ")
    cat(paste("**",params$main_log2fold.day,"**.",sep=""))

    if (params$main_log2_interpolate) {
        print("Data were interpolated for this plot.")
    }

```

### Hybrid Waterfall Plot

```{r hybrid waterfall, fig.align='center', echo=FALSE}

    plot_data <- params$data_subset

    if (params$main_tc_interpolate){
        plot_data <- get_interpolated_pdx_data(data = plot_data)
        plot_data$Volume <- plot_data$Interpolated_Volume
    }

    tc_ratios <- T.C_ratio(plot_data, last.measure.day = params$main_TC.day)

    WaterfallPlot_Hybrid(tc_ratios)

    params$progress$inc(1 / 10)
```

```{r hybrid waterfall plot option text, results='asis', echo=FALSE}

    cat("The hybrid waterfall plot was computed on (or near) day: ")
    cat(paste("**",params$main_TC.day,"**.",sep=""))

    if (params$main_tc_interpolate) {
        print("Data were interpolated for this plot.")
    }

```

### Tumor Growth Inhibition

\captionsetup[table]{labelformat=empty}

```{r TGI, results='asis', fig.align='center', echo=FALSE}

    plot_data <- params$data_subset

    if (params$main_tgi_interpolate){
        plot_data = get_interpolated_pdx_data(data = plot_data)
        plot_data$Volume <- plot_data$Interpolated_Volume
    }

    tc_ratios <- T.C_ratio(plot_data, last.measure.day = params$main_TGI.day)

    #plot_measure = c('TC.ratio', 'aov.TC.ratio')
    plotTC.ratio(tc_ratios, plot_measure = 'aov.TC.ratio' )
    # NOTE: aov.TC.ratio is used in manuscript.


    response_list = list()

    response_list <- T.C_ratio(plot_data, last.measure.day = params$main_TGI.day)

    response_list <- response_list %>% dplyr::select(-mean.TVratio,	-var.TVratio,	-mean.dVt, -TC.ratio) %>%
                                dplyr::select(Contributor, Study, Tumor, Arms, TC.CalcDay, n.TVratio, aov.TC.ratio, se_TC.ratio, Contrast.pValue) %>%
                                dplyr::rename(pValue = Contrast.pValue)

    if (knitr::is_latex_output()) {
        kable(response_list[order(response_list$Arms),], digits=2, row.names = FALSE, align = "c", format="latex", booktabs=T, linesep = "", caption = "Tumor Growth Inhibition Summary Table") %>% 
            kable_styling(latex_options=c("hold_position", "scale_down"), font_size = 10, html_font = "Times New Roman")
    } else {
        kable(response_list[order(response_list$Arms),], digits=2, row.names = FALSE, booktabs=T, caption = "Tumor Growth Inhibition Summary Table") %>%
            kable_styling(full_width = TRUE, position = "left")
    }

    params$progress$inc(1 / 10)
```

```{r TGI option text, results='asis', echo=FALSE}

    cat("Tumor growth inhibition was computed on (or near) day: ")
    cat(paste("**",params$main_TGI.day,"**.",sep=""))

    if (params$main_tgi_interpolate) {
        print("Data were interpolated for this plot.")
    }

```

### Stacked ORC Plot

```{r Stacked ORC Plot, fig.align='center', echo=FALSE}

    plot_data <- params$data_subset

    if (params$main_stackedorc_interpolate){
        plot_data <- get_interpolated_pdx_data(data = plot_data)
        plot_data$Volume <- plot_data$Interpolated_Volume
    }

    vc_change <- IndividualMouseResponse(plot_data, last.measure.day = params$main_orc.day)

    plotStackedORC(vc_change)

    params$progress$inc(1 / 10)
```

```{r stacked ORC option text, results='asis', echo=FALSE}

    cat("Objective response was computed on (or near) day: ")
    cat(paste("**",params$main_orc.day,"**.",sep=""))

    if (params$main_stackedorc_interpolate) {
        print("Data were interpolated for this plot.")
    }

```

\newpage

## Individual Study Plots & Analysis

### Individual Study ORC Analysis

\captionsetup[table]{labelformat=empty}

```{r individual study ORC table, fig.align='center', results='asis', echo=FALSE, out.width="50%"}

    plot_data <- params$data_subset
    
    response_list = list()

    for (study in levels(as.factor(plot_data$Study))) {

        df <- base::subset(
            plot_data, Study %in% c(study)
        )

        df <- droplevels(df)

        if (params$tv_interpolate){
            df = get_interpolated_pdx_data(data = df)
            df$Volume <- df$Interpolated_Volume
        }

        study <- unlist(levels(factor(df$Study)))[1]

        filtered.df <- df %>%
        filter(Study == study) %>% droplevels()

        response_list[[study]] <- get_response_level(filtered.df, last.measure.day = params$recist.day)$Response.Level
        response_list[[study]]$Study <- study

        if ('Control'%in%unique(response_list[[study]]$Arms)){
        response_list[[study]]$Arms <- relevel(factor(response_list[[study]]$Arms), 'Control')
        }

        response_list[[study]]$Response.Level <- factor(response_list[[study]]$Response.Level)

        response_list[[study]] <- response_list[[study]] %>% dplyr::select('Study', 'Tumor', 'Arms', 'Best.Response', 'Avg.Response', 'Response.Level')
    }

    output_response <- bind_rows(response_list)

    if (knitr::is_latex_output()) {
        kable(output_response[order(output_response$Study, output_response$Arms),], digits=2, row.names = FALSE, align = "c", format="latex", booktabs=T, linesep = "", caption = "Cross Study Objective Response Criteria") %>% 
            kable_styling(latex_options=c("hold_position", "scale_down"), font_size = 10, html_font = "Times New Roman")
    } else {
        kable(output_response[order(output_response$Study, output_response$Arms),], digits=2, row.names = FALSE, caption = "Cross Study Objective Response Criteria") %>%
            kable_styling(full_width = TRUE, position = "left")
    }

    params$progress$inc(1 / 10)
```

```{r individual study ORC option text, results='asis', echo=FALSE}

    cat("Objective response was computed on (or near) day: ")
    cat(paste("**",params$tv_recist.day,"**.",sep=""))

    if (params$tv_interpolate) {
        print("Data were interpolated for this analysis.")
    }

```

\newpage

### Individual Animal Waterfall Plot(s)

```{r individual study waterfall option text, results='asis', echo=FALSE}
    cat("Waterfall plot(s) were generated using the metric: ")
    cat(paste("**",params$waterfall_metric,"**, ",sep=""))

    if (params$waterfall_metric == 'AUC.Filtered.Measures') {
        cat("on (or near) day: ")
        cat(paste("**",params$tv_AUC.day.waterfall,"**.",sep=""))
    } else {
        cat("at study end.")
    }

    if (params$tv_waterfall_interpolate) {
        print("Data were interpolated for this (these) plot.")
    }

```

```{r individual study waterfall, fig.align='center', results='asis', echo=FALSE}

    for (study in levels(as.factor(plot_data$Study))) {

        cat("\n\n#### Study: ", study, "\n")

        df <- params$data_subset %>% dplyr::filter(Study == study)
                
        df <- droplevels(df)

        study <- unlist(levels(factor(df$Study)))[1]

        filtered.df <- df %>%
        dplyr::filter(Study == study) %>% droplevels()

        if (params$tv_waterfall_interpolate) {
            filtered.df = get_interpolated_pdx_data(data = filtered.df)
            filtered.df$Volume <- filtered.df$Interpolated_Volume
        }

        resp <- IndividualMouseResponse(filtered.df, last.measure.day = params$tv_AUC.day.waterfall)

        print(WaterfallPlot_PDX(resp, params$waterfall_metric))

        cat("\n\n\\newpage\n")
    }
    params$progress$inc(1 / 10)
```

\newpage

### Event Free Survival Analysis

```{r individual study EFS option text, results='asis', echo=FALSE}
    cat("Event free survival analysis was computed using the event size (percent Change in volume) of: ")
    cat(paste("**",params$tv_PercChange_EventSize,"**.",sep=""))
```

```{r EFS, fig.align='center', results='asis', echo=FALSE}

    for (study in levels(as.factor(plot_data$Study))) {

        cat("\n\n#### Study: ", study, "\n")

        df <- params$data_subset %>% dplyr::filter(Study == study)
             
        df <- droplevels(df)

        study <- unlist(levels(factor(df$Study)))[1]

        filtered.df <- df %>%
        dplyr::filter(Study == study) %>% droplevels()

        print(EFSplot(filtered.df, params$tv_PercChange_EventSize))

        cat("\n\n\\newpage\n")
    }    

    params$progress$inc(1 / 10)
```

\newpage

### ANOVA

```{r individual ANOVA option text, results='asis', echo=FALSE}
    cat("ANOVA was conducted on (or near) day: ")
    cat(paste("**",params$anova_Measure_Day,"**.",sep=""))

    if (params$main_anova_interpolate) {
        print("Data were interpolated for this analysis.")
    }
```

\captionsetup[table]{labelformat=empty}

```{r ANOVA, results='asis', echo=FALSE}

    for (study in levels(as.factor(plot_data$Study))) {

        cat("\n\n#### Study: ", study, "\n")

        df <- params$data_subset %>% dplyr::filter(Study == study)

        df <- droplevels(df)     

        for (tumor in levels(as.factor(df$Tumor))) {

            cat("\n\n##### Tumor: ", tumor, "\n")

            aov_res <- response_analysis(params$data_subset,
                    method = 'endpoint.ANOVA', 
                    last.measure.day = params$anova_Measure_Day, 
                    multi_test_anova = FALSE, 
                    tv_study_filtered = study, 
                    tv_tumor_filtered = tumor, 
                    main_anova_interpolate = params$main_anova_interpolate,
                    report = TRUE)
    
            if(is.null(aov_res)) {
            
                cat("\n\nANOVA failed. This is likely due to an invalid study day selection (i.e., study day selected beyond end of available study dates).\n\n") 
            
            } else {

                mct <- as.data.frame(aov_res$mct[['Arms']])
                mct$'diff' <- round(mct$'diff', digits=2)
                mct$'lwr' <- round(mct$'lwr', digits=2)
                mct$'upr' <- round(mct$'upr', digits=2)
                mct$'p adj' <- round(mct$'p adj', digits=4)

                if (knitr::is_latex_output()) {

                    print(knitr::kables(
                    list(
                    # the first kable() to change column names
                    knitr::kable(aov_res$anova[[1]], digits=2, format="latex", booktabs=T, linesep = "", valign = 't'),
                    # the second kable() to set the digits option
                    knitr::kable(mct, digits=2, format="latex", booktabs=T, linesep = "", valign = 't')
                    ),
                    caption = 'ANOVA and Tukey multiple means comparsion test tables'
                    ))

                    cat("\n\n###### \n")

                } else {
                    cat(kable(aov_res$anova[[1]], digits=2, caption = "ANOVA table") %>%
                    kable_styling(full_width = FALSE, position = "float_left"))

                    cat(kable(mct, digits=2, caption = "Tukey multiple means comparsion test") %>%
                    kable_styling(full_width = FALSE, position = "left"))

                    cat(kable(mct[0,], digits=2, col.names = NULL, row.names = FALSE) %>%
                    kable_styling(full_width = TRUE))
                    # An empty table is required to break the 'float_left'. Without this table, the next header wraps to the right side of the screen. 

                    cat("\n\n###### \n")
                    
                }
                
                cat("\n\n")
            }
            
            cat("\n\n")
        }
    }
    params$progress$inc(1 / 10)
```

### Body Weight Plots

```{r check_weight_available, echo=FALSE}
    if ("Body_Weight" %in% names(params$data_subset)) {
        if (all(is.na(params$data_subset$Body_Weight)) | all(is.null(params$data_subset$Body_Weight))) {
            weight_plots_available <- FALSE
            cat("Body weights not provided.")
        } else {
            weight_plots_available <- TRUE
        }
    } else {
        weight_plots_available <- FALSE
        cat("Body weights not provided.")
    }
```

```{r Body Weight Plot, fig.align='center', echo=FALSE, eval=weight_plots_available}
    #   # Get Level Type Input by User
    if (params$tv_weight_plot_type == "Treatment Plot") {
        pattern_type <- "Treatment"
    } else if (params$tv_weight_plot_type == "Study Plot") {
        pattern_type <- "Study"
    }

    if (params$tv_weight_plot_style == "Study Average") {
        level_type <- "Arm"
    } else if (params$tv_weight_plot_style == "Individual Animal") {
        level_type <- "Animal"
    }

    if (params$tv_weight_plotType == 'Percent Change'){
        data <- params$data_subset %>%
            dplyr::arrange(Study, Tumor, Arms, ID, Times) %>%
            dplyr::group_by(Study, Tumor, Arms, ID) %>%
            dplyr::mutate(dWeight = (((Body_Weight - Body_Weight[1]) / Body_Weight[1] ) * 100))

        data$Body_Weight <- params$data$dWeight
    } else {
        data <- params$data_subset
    }
    #   # Call plot
    get_weight_plot(data = data, level = level_type, pattern = pattern_type, position.dodge = 0.2, tv_weight_plotType = params$tv_weight_plotType)
    
    params$progress$inc(1 / 10)
```

```{r weight plot option text, results='asis', echo=FALSE, eval=weight_plots_available}

    cat("The response plot metric: ")
    cat(paste("**",params$tv_weight_plotType,"**",sep=""))
    cat(", was faceted by: ")
    cat(paste("**",params$tv_weight_plot_type,"**",sep=""))
    cat(", plots were organized by: ")
    cat(paste("**",params$tv_weight_plot_style,"**. ",sep=""))

```

\newpage

## Session Info
<!-- https://stackoverflow.com/a/65630773/18557826 -->

### R environment used in session

\renewcommand{\arraystretch}{0.8} <!-- decrease line spacing for the table -->
```{r Reproducibility-SessionInfo-R-environment, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
    suppressPackageStartupMessages({
        library("devtools")
        library("tibble")
    })
    
    df_session_platform <- devtools::session_info()$platform %>% 
    unlist(.) %>% 
    as.data.frame(.) %>% 
    rownames_to_column(.)

    colnames(df_session_platform) <- c("Setting", "Value")

    if (knitr::is_latex_output()) {
        kable(df_session_platform, row.names = FALSE, align = "c", format="latex", booktabs=T, linesep = "") %>% 
        kable_styling(latex_options=c("hold_position"), full_width = F, font_size = 10, html_font = "Times New Roman")
    } else {
        kable(df_session_platform, booktabs = T, align = "c") %>% 
        kableExtra::kable_styling(full_width = F, latex_options = c("hold_position"))
    }

```
\renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->

### R Packages used in session

\renewcommand{\arraystretch}{0.6} <!-- decrease line spacing for the table -->

```{r Reproducibility-SessionInfo-R-packages, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
    df_session_packages <- devtools::session_info()$packages %>% 
    as.data.frame(.) %>% 
    filter(attached == TRUE) %>% 
    dplyr::select(loadedversion, date) %>% 
    rownames_to_column

    colnames(df_session_packages) <- c("Package", "Loaded version", "Date")

    if (knitr::is_latex_output()) {
        kable(df_session_packages, row.names = FALSE, align = "c", format="latex", booktabs=T, linesep = "") %>% 
        kable_styling(latex_options=c("hold_position"), full_width = F, font_size = 10, html_font = "Times New Roman")
    } else {
        kable(df_session_packages, booktabs = T, align = "c") %>% 
        kableExtra::kable_styling(full_width = F, latex_options = c("hold_position"))
    }

```
\renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->